The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-01 analysis/paper/paper.qmd

# Geocode thesis locations
emu_theses <- emu_theses %>%
  geocode(location, method = 'osm', lat = latitude , long = longitude)

# Show thesis locations on world map
world <- ggplot2::map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_count(data = emu_theses, aes(longitude, latitude), color = "red", alpha = 0.7) +
  scale_size_area(max_size = 3) +
  coord_fixed() +
  theme_void()
```

>>>>

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses, location = NULL)

# emu_theses <- tidygeocoder::geocode(
#   emu_theses,
#   address = location,
#   method = 'osm',
#   lat = latitude ,
#   long = longitude
# )

# Show thesis locations on world map
visualize_thesis_locations(emu_theses)
```
